Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-12-15 Paper/ms.tex
More work on simulated data section

We ran the MCMC on the simulated dataset to obtain the posterior distribution
for the model parameters. The posterior distribution for $N$, the number of
planets, is shown in Figure~\ref{fig:fake_data_N}. The true number of planets,
5, is also the most probable value according to the posterior distribution,
simply by chance. The posterior distribution also suggests that $N=4$ has
substantial probability.
The posterior distribution for the periods $\{P_i\}_{i=1}^N$ is shown in
Figure~\ref{fig:fake_data_periods}. Because of the label switching degeneracy,
the posterior distribution for each period is identical, so we pooled the
results for all periods. Defining the log-periods by
$S_i =  \log_{10}\left[P_i/(\textnormal{1 day})\right]$,
Figure~\ref{fig:fake_data_periods} is a Monte Carlo representation
of the mixture distribution
\begin{eqnarray}
f(S) &=& \sum_{N=0}^{10} p(N | D)\sum_{i=1}^N p(S_i | N, D).
\end{eqnarray}
The posterior distribution for the periods, shown in
Figure~\ref{fig:fake_data_periods}, shows that four of the true periods were
recovered, with probability close to 1. One period which was actually present
was not detected because it had a very small amplitude. There is also some
evidence for periods which did not exist, however the posterior probabilities
for these peaks are not close to 1.

@@

\begin{figure}
\includegraphics[scale=0.4]{Figures/fake_data_periods.eps}
\caption{The posterior distribution for the periods\label{fig:fake_data_periods}}
\end{figure}

\begin{figure}
\includegraphics[scale=0.4]{Figures/fake_data_posterior.eps}
\caption{\label{fig:fake_data_posterior}}
\end{figure}

>>>>

We ran the MCMC on the simulated dataset to obtain samples from the
posterior distribution. We obtained 590 samples.
The posterior distribution for $N$, the number of
planets, is shown in Figure~\ref{fig:fake_data_N}. The true number of planets,
5, is also the most probable value according to the posterior distribution,
simply by chance. The posterior distribution also suggests that $N=4$ has
substantial probability.
The posterior distribution for the periods $\{P_i\}_{i=1}^N$ is shown in
Figure~\ref{fig:fake_data_periods}. Because of the label switching degeneracy,
the posterior distribution for each period is identical, so we pooled the
samples for all periods. Defining the log-periods by
$S_i =  \log_{10}\left[P_i/(\textnormal{1 day})\right]$,
Figure~\ref{fig:fake_data_periods} is a Monte Carlo representation
of the mixture distribution
\begin{eqnarray}
f(S) &=& \sum_{N=0}^{10} p(N | D)\sum_{i=1}^N p(S_i | N, D).
\end{eqnarray}
The posterior distribution for the periods, shown in
Figure~\ref{fig:fake_data_periods}, shows that four of the true periods were
recovered, with probability close to 1. One period (with $\log_{10}P_i \approx 1.8$)
which was actually present was not ``detected'' because it had a very small
amplitude. We note that the posterior probability near this period should not be
precisely zero. There is also some
evidence for periods which did not actually exist, however the posterior
probabilities for these peaks are not close to 1.

@@

\begin{figure}
\includegraphics[scale=0.4]{Figures/fake_data_periods.eps}
\caption{The posterior distribution for the periods given the simulated
dataset. The solid lines are the true periods, four of which were detected
with high posterior probability.\label{fig:fake_data_periods}}
\end{figure}

The joint posterior distribution for the periods and the amplitudes of the
signals is shown in Figure~\ref{fig:fake_data_posterior} along with the
eccentricities. As with Figure~\ref{fig:fake_data_periods}, the samples for
all planets were combined. The true values are also plotted as circles. Clearly, the
reason the period of $\log_{10}(P_i) \approx 1.8$ was not ``detected'' was that
it had a very low amplitude of approximately 1 m s$^{-1}$ which is one fifth
of the noise level.

\begin{figure}
\includegraphics[scale=0.4]{Figures/fake_data_posterior.eps}
\caption{The joint posterior distribution for the periods and the amplitudes
(top panel) and the periods and eccentricities (bottom panel).
\label{fig:fake_data_posterior}}
\end{figure}
